Estimating length of SARS-CoV-2 from doubly interval censored data with missed infections

### 2024-03-25 paper-surv-analysis.tex
proof ch 5

The CIS had a household-based design inviting all individuals aged 2 and over from selected households.
Once invited, an enrollment swab would be taken at the first visit followed by 4 further weekly visits (giving a total of 5 swabs on days 0, 7, 14, 21, 28 relative to enrollment) after which visits were monthly.
Swabs were tested for the presence of SARS-CoV-2 using RT-PCR.
In reality, visits were often not on this precise schedule, and occasionally missed.
A full description of the study can be found in the study protocol~\autocite{cisProtocol}.

>>>>

The CIS had a household-based design inviting all individuals aged 2 and over from selected households.
Once invited, an enrolment swab would be taken at the first visit followed by 4 further weekly visits (giving a total of 5 swabs on days 0, 7, 14, 21, 28 relative to enrolment) after which visits were monthly.
Swabs were tested for the presence of SARS-CoV-2 using RT-PCR.
In reality, visits were often not on this precise schedule, and occasionally missed.
A full description of the study can be found in the study protocol~\autocite{cisProtocol}.
